Worflow

### 2017-06-13 R/workflow.Rmd
Corrected RSEC code

```{r rsec_50}
fn <- '../data/RSEC_W.rda'
if (runClus & !file.exists(fn)){
  #symbol for samples missing from original clustering
  seObj <- SummarizedExperiment(t(W), colData = colData(core))
  print(system.time(ceObj <- RSEC(seObj, k0s = 4:15, alphas = c(0.1),
                                  betas = 0.8,
                clusterFunction = "hierarchical01", minSizes=1,
                ncores = NCORES, isCount=FALSE,
                subsampleArgs = list(resamp.num=100,
                                     clusterFunction="kmeans",
                                     clusterArgs=list(nstart=10)),
                seqArgs = list(k.min=3, top.can=5), verbose=TRUE,
                combineProportion = 0.7,
                mergeMethod = "none")))
  save(ceObj, file = fn)
}else{
  load(fn)
}
```

@@

```{r heatmaps}
# sampleData <- data.frame(ours = primaryCluster(ceObj))
# plotHeatmap(assays(se)$normalizedValues,
#             main = 'Normalized values, 1000 most variable genes',
#             clusterSamplesData = ceObj@dendro_samples,
#             sampleData = as.matrix(sampleData),clusterLegend=ceObj@clusterLegend[1])
# easier fix:
origClusterColors<-bigPalette[1:nlevels(colData(ceObj)$clusterLabels)]
experimentColors<-bigPalette[1:nlevels(colData(ceObj)$Experiment)]
batchColors<-bigPalette[1:nlevels(colData(ceObj)$Batch)]
metaColors<-list("Experiment"=experimentColors,"Batch"=batchColors,"clusterLabels"=origClusterColors)

@@

Cluster name | Description | Correspondence
-------------|-------------|-----------------
c1 | HBC | original 1, 5
c2 | new and small | new and small
c3 | new and small | new and small
c4 | GBC / immature neurons / MV 1 | original 2, 3, 11, 14
c5 | Sus | original 4, 7
c6 | Neuron | original 9, 12
c7 | Immature Neuron | original 10, 14
c8 | Immature Neuron | original 14
c9 | Microvillus | original 15

@@

K = 3 does not seem very good to me: Sus is not an end cluster, GBC is an end cluster.

K = 4 is better, slingshot finds the end clusters but there is a spurious end cluster.

K = 5 does not seem great to me: GBC is an end cluster and Sus and Microvillus are in the same lineage.

@@

K = 3 finds GBC as an end cluster (that I did not specify in the end.clus!).

K = 4 Yeah! it seems that it is what we want even if we still have a spurius end cluster and GBC not really at the junction.

K = 5 Yeah! even if GBC not really at the junction.

@@

@@

### Re-fitting zinbwave
#### Unsupervised

K = 3 is better than when we did not refit zinbwave but still not perfect: Sus in all the clusters. GBC not really at the junction.

K = 4 good even if GBC not really at the junction.

K = 5 not great GBC is an end cluster.

```{r refit_zinb, eval=FALSE}
fn <- '../data/refit_zinbwave_slingshot.rda'

@@

```{r slingshot_unsup_refit, eval=FALSE}
for(k in Kvec) {
  X <- getW(zinbList[[k - 2]])[, 1:k]

@@

K = 3 Yeah! close to perfection.

K = 4 good even if GBC not really at the junction.

K = 5 no, GBC is an end cluster.

```{r slingshot_sup_refit, eval=FALSE}
for(k in Kvec){
  X <- getW(zinbList[[k - 2]])[, 1:k]

>>>>

```{r rsec_50}
fn <- '../data/RSEC_W.rda'
if (runClus & !file.exists(fn)){
  #symbol for samples missing from original clustering
  seObj <- SummarizedExperiment(t(W), colData = colData(core))
  print(system.time(ceObj <- RSEC(seObj, k0s = 4:15, alphas = c(0.1),
                                  betas = 0.8, dimReduce="none",
                clusterFunction = "hierarchical01", minSizes=1,
                ncores = NCORES, isCount=FALSE,
                subsampleArgs = list(resamp.num=100,
                                     clusterFunction="kmeans",
                                     clusterArgs=list(nstart=10)),
                seqArgs = list(k.min=3, top.can=5), verbose=TRUE,
                combineProportion = 0.7,
                mergeMethod = "none", random.seed=424242)))
  save(ceObj, file = fn)
}else{
  load(fn)
}
```

@@

```{r heatmaps}
# sampleData <- data.frame(ours = primaryCluster(ceObj))
# plotHeatmap(assays(se)$normalizedValues,
#             main = 'Normalized values, 1000 most variable genes',
#             clusterSamplesData = ceObj@dendro_samples,
#             sampleData = as.matrix(sampleData),clusterLegend=ceObj@clusterLegend[1])
# easier fix:
colData(ceObj)$clusterLabels <- as.factor(colData(ceObj)$clusterLabels)
origClusterColors<-bigPalette[1:nlevels(colData(ceObj)$clusterLabels)]
experimentColors<-bigPalette[1:nlevels(colData(ceObj)$Experiment)]
batchColors<-bigPalette[1:nlevels(colData(ceObj)$Batch)]
metaColors<-list("Experiment"=experimentColors,"Batch"=batchColors,"clusterLabels"=origClusterColors)

@@

Cluster name | Description | Color | Correspondence
-------------|-------------|-------| ----------
c1 | HBC | blue | original 1, 5
c2 | GBC / immature neurons / MV 1 | green | original 2, 3, 11
c3 | Sus | red | original 4, 7
c4 | Neuron | orange | original 9, 12
c5 | Immature Neuron | purple | original 10, 14
c6 | new and small | brown | original 9
c7 | Microvillus | cyan | original 15

@@

K = 3 only one lineage: sus is right after HBC

K = 4 two lineages: sus is right after HBC, differ only in end point (neuron, new cluster)

K = 5 three lineages: hbc-gbc-immature neuron-new-neuron; hbc-gbc-mv; hbc-sus (perfect!)

@@

K = 3 four lineages: might be good, three lineages are correct and the fourth is plausible.

K = 4 same as K=3

K = 5 same as K=3

@@

  lineages <- get_lineages(X, clus.labels = cl, start.clus = "c1",
                           end.clus = c("c3", "c6", "c7"))
  curves <- get_curves(X, clus.labels = cl, lineages = lineages)
  plot_curves(X, cl, curves, col.clus = pal)
  plot_tree(X, cl, lineages, col.clus = pal)

@@

### Re-fitting zinbwave

K = 3 four lineages: immature neurons as a end point (not good)

K = 4 same as K = 3

K = 5 same as K = 3

```{r refit_zinb}
fn <- '../data/refit_zinbwave_slingshot.rda'

@@

```{r slingshot_unsup_refit}
for(k in Kvec) {
  X <- getW(zinbList[[k - 2]])[, 1:k]

@@

K = 3 four lineages (the small new cluster is still an end point)

K = 4 same as K=3

K = 5 three lineages (correct)

```{r slingshot_sup_refit }
for(k in Kvec){
  X <- getW(zinbList[[k - 2]])[, 1:k]
